\specialhead{ACKNOWLEDGMENT}
My seven year mission to seek out new methods for load balancing and building
unstructured mesh workflows was a team effort.
First and foremost, my family and my fiance Alysia provided the much-needed love
and moral support to get through long hours, travel, and times of high stress.
My colleagues Dan Ibanez, Brian Granzow, Seegyoung Seol, Gerrett Diamond, Dan
Zaide, Ben Matthews, Michel Rasquin and many others collectively provided
excellent technical support and devoted many hours to help advance my work.
When my colleagues and I couldn't work out a bug or conceptual issue professors
Ken Jansen, Onkar Sahni, Chris Carrothers, and Scientific Computation Research
Center (SCOREC) research staff member Max Bloomfield provided precious chunks of
their time to help.

Development, testing, and large scale runs were made possible by the staff and
system administrators at the Texas Advanced Computing Center, Argonne National
Laboratory, the SCOREC (Ben Matthews, Tim McMullan and Tim Wickberg), and the
Computational Center for Innovations (Lindsay Todd, Dan Weeks, and Derek Fox)
who kept the software and hardware systems running and up to date.

Thank you to my committee for mentoring me through the Ph.D. program and
reviewing my work.

Last, but not least, thanks to my adviser and boss Mark Shephard for leading my
professional development as a full-time staff member and my research as a
part-time graduate student.
Mark's guidance for navigating complex research topics and, at times, even more
complex institutional bureaucracies, was critical to my success.
